Order reduction and MILP models for certifying Robustness of DNNs globally.

### 2025-07-31 AAAI2026/experiments.tex
exp

	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
	for an $L_1$-deformation $\leq .5$. The pipe considers a mixture of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
	maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.

For each benchmark, we report three value: the bound obtained (lower value is better),
the solution obtained (distance to the bound depicts how close the model has converged),
and worst-case (higher is better) which is taking the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
the worst-case will equal the solution, otherwise, it will be smaller.

@@

We start by evaluating how accurate the 2v model is vs the classical encoding, both when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly. We use the pipe models which is easier to handle, and set the time-out at 1000s for both models.

@@

We confirm both that the LP relaxation of the classical model is extremely poor, with bounds 8 times worst than using our "2v" model. Further, even using a fully accurate mode with all 100x2 variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.

>>>>

	MNIST is a classification benchmark, we thus report different bound $\beta^{\epsilon}_{i,j}$
	for an $L_1$-deformation $\leq .5$. The pipe considers a conjunction of $L_1 \leq 3.9$ and $L_\infty \leq 0.2$ perturbations, corresponding to physically pertinent dimensions, and 
	maximizes the sum of the difference in output of 10 selected points in the mesh between an input and its deformation.

For each benchmark, we report three value: the bound obtained (lower value is better),
the solution obtained (distance to the bound depicts how close the model has converged),
and worst-case (higher is better) which is taking the solution as input to the DNN. For a fully accurate model ("2v" or classical and all variables binary),
the worst-case will equal the solution, otherwise, it will be smaller due to abstraction.

@@

We start by evaluating how accurate the 2v model is vs the classical encoding, both when half the ReLUs are approximated with the LP relaxation, and when all the ReLUs are encoded exactly. We use the pipe models which is easier to verify, and set the time-out at 1000s for both models.

@@

We confirm that the LP relaxation of the classical model is extremely poor, with bounds $8$ times worse than using our "2v" model. Further, even using a fully accurate model with all $100 \times 2$ variables encoded as binary variables, the "2v" model produces bounds $>4$ times better than the classical model, due to the internal Branch and Bound process to compute bounds, which uses linear relaxation.
